VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-18 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
newest version

 \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
 \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}

@@

%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}

Text of the abstract. Text of the abstract. Text of the abstract.
Text of the abstract. Text of the abstract. Text of the abstract.
Text of the abstract. It should give a comprehensive idea about the
paper's subject and the author's results. The Abstract (and the first 2 pages of the paper) will be
available free at DeGryuter's website for the journal.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Section 1 %%%%%%%%%%%%%
%\section{Introduction}\label{Sec:1}

\section{First section of the paper}\label{sec:1}

\setcounter{section}{1}
\setcounter{equation}{0}\setcounter{theorem}{0}

Text ... (for details, see \cite{GasRah}, \cite{Rosbl}, \cite{Kir},
\cite{Moak}) ...

%%%% example of definition %%%%
 \begin{definition}\label{Def3}
Text of Definition~\ref{Def3}.
 \end{definition}

   \vspace*{-12pt} %%% example of subsection:
 \subsection{Preliminary results}\label{subsec:1.1}

%%%% example of theorem %%%%%%%%%%
 \begin{theorem}\label{Th1}
Text of Theorem~\ref{Th1} ....
 \end{theorem}

 \proof %%%%%%%%%%%%%
 Give here the proof of Theorem~\ref{Th1}. Example for
equation:
\begin{equation}\label{eq1}
ax^2+bx +c =0.
\end{equation}
 As seen by equation \eqref{eq1}, it is ...
 The proof follows from Ref. \cite{Moak}.
 \proofend %%%%%%%%%%

%%%% example of corollary %%%%
 \begin{corollary}\label{Cor2}
Text of Corollary~\ref{Cor2} ....
 \end{corollary}

 \proof
 Here comes the proof of Corollary~\ref{Cor2}.
 \proofend

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Second section of the paper}\label{sec:2}

\setcounter{section}{2}
\setcounter{equation}{0}\setcounter{theorem}{0}

 Text ... As seen in Section~\ref{sec:1}, the equation
(\ref{eq1}), $ a\neq 0$, has the solutions
 \begin{equation}\label{eq2}
 x_{1,2}= {\frac {-b \pm \sqrt{b^2-4ac}}{2a}}\,.
 \end{equation}

 %%% example of example %%%%%
 \begin{example}\label{Ex1}
 Let us take in (\ref{eq2}) ... Then, by Theorem~\ref{Th1}, ...
 \end{example}

 \begin{example}\label{Ex2}
 Under same conditions as in Example~\ref{Ex1}, we consider ...
 \end{example}

The figures should be input in the LaTeX file as eps-files, as below:

%%%%%%%%% example for figure %%%%%%%%%%%%%%%%%%%
  \begin{center}
  \includegraphics[scale=0.4]{figure.eps}
 % \hspace*{2cm}
 % \includegraphics[scale=0.7]{figure2.eps}

 \bigskip

  Fig. 2.1: Control loop
  \end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 Often figures include texts or Latin, Greek etc. letters.
 We kindly ask the authors to take care that no texts fonts need to be embedded, by saving first the text as curves.
 Just in case, along with the obligatory eps-files, please send us also some alternative figures' files in  pdf-, jpg-, etc. format.

\section{Riemann-Stieltjes integral}
Let $f$ and $g$ denote real-valued functions defined on a closed interval $[a',b']$ of the real line. We shall suppose that both $f$ and $g$ are bounded on $[a',b']$. These assertions are assumed to be true throughout the paper and will not be repeated again.

\begin{definition}
Define a partition $\mathcal{P}$ of $[a',b']$ to be a set of points $x_0, x_1,\cdots,x_n$, 
where $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$. For each partition 
$\mathcal{P}$ of $[a',b']$ write $\Delta g_k = g(x_k)-g(x_{k-1})$. Let 
$M_k = \sup\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \inf\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
\begin{equation}
\label{ref:S_up}
\mathcal{S}_U(\mathcal{P},f,g) = \sum_{k=1}^n M_k \Delta g_k, 
\end{equation}
and
\begin{equation}
\label{ref:S_low}
\mathcal{S}_L(\mathcal{P},f,g) = \sum_{k=1}^n m_k \Delta g_k. 
\end{equation}
The sums in Eq.~\eqref{ref:S_up} and Eq.~\eqref{ref:S_low} are respectively called the the upper and lower Riemann-Stieltjes sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{S}_L(\mathcal{P},f,g)\leq I \leq \mathcal{S}_U(\mathcal{P},f,g)$ for all 
partitions $P$ of $[a',b']$, then $f$ is Riemann integrable with respect to $g$ on $[a',b']$. Moreover, $I$ is called the Riemann-Stieltjes integral of $f$ from $a'$ to $b'$ and is denoted by
\begin{equation}
\int_{a'}^{b'} f(x) dg(x). 
\end{equation}
\end{definition}

\begin{theorem}
If the derivative $g'$ exists and is continuous on $[a',b']$ and if $f$ is integrable with respect to $g$ on $[a',b']$, then the following 
Riemann and Riemann-Stieltjes integrals are equivalent
\begin{equation}
\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)dx.
\end{equation}
\end{theorem}

@@

Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
integration strip is calculated using Cavalieri's principle. Cavalieri's principle is stated below without proof:
\begin{theorem}
Suppose two regions in a plane are included between two parallel lines in that plane. If every line parallel to these
two lines intersects both regions in line segments of equal length, then the two regions have equal areas. NEED CITATION
\end{theorem}
The definition of the Cavalieri integral is presented in Definition~\ref{def:cav_integral}.
It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader who is not familiar with the Cavalieri integral should only refer back to the definitions 
presented in this section when things in Section~\ref{??} become unclear. Moreover, the definitions presented below were taken from [?]. Furthermore, none of the theorems in this section are proved, the proofs can be found in [].

@@

Let $a(y)$ be a translational function with respect to a real--valued function $f(x)$ on the interval $[a,b]$. Moreover, $b(y) = a(y) + (b-a)$. Furthermore, the functions $a(y)$ and $b(y)$ intersect $f(x)$ at $a'$ and $b'$ respectively.
These assertions are assumed to be true throughout the paper and will not be repeated again.

@@

\noindent
The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively.

\begin{definition}\label{def:cav_integral}
Define a partition $\mathcal{P}_1$ of $[a,b]$ to be a set of points $x_0^1, x_1^1,\cdots,x_n^1$, 
where $a = x_0^1 \leq x_1^1 \leq \cdots \leq x_n^1 = b$. For each partition 
$\mathcal{P}_1$ of $[a,b]$ write $\Delta x_k^1 = x_k^1-x_{k-1}^1$. 
%Since both boundaries of any integration strip are necessarily
%translations of the translational function $a(y)$, we can apply the transformation
%function $h$ to the partition $\mathcal{P}_1$. 
If the transformation function $h$ is strictly increasing,
the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. It
can be assumed that $h$ is strictly increasing, without any loss of generality.  Let 
$M_k = \sup \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, $m_k = \inf \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, and set 
\begin{equation}
\label{eq:c_up}
\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k^1, 
\end{equation}
and
\begin{equation}
\label{eq:c_low}
\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k^1. 
\end{equation}
The sums in Eq.~\eqref{eq:c_up} and Eq.~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{C}_L(\mathcal{P}_1,f,h)\leq I \leq \mathcal{C}_U(\mathcal{P}_1,f,h)$ for all 
partitions $\mathcal{P}_1$ of $[a,b]$, then $I$ is called the Cavalieri integral of $f$ from $a(y)$ to $b(y)$ and is denoted by
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx.
\end{equation}
\end{definition}

Note that the superscripts of the $x$-coordinates in the above definitions indicate to which partition, either $\mathcal{P}_1$ or $\mathcal{P}_2$, the $x$-coordinate in question belongs.

\begin{theorem}
\label{t:conv}
The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent:
\begin{equation}
\int_{a(y)}^{b(y)} f(x)\,dx = \int_a^b f\circ h(x)\,dx = \int_{a'}^{b'} f(x)\,dg(x),
\end{equation}
with $g(x) = x-a\circ f(x) + a$ and $h(x) = g^{-1}(x)$.
\end{theorem}

Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral?

Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$. Moreover, recall that 
\begin{equation}
\label{eq:g_def2}
g(x) = x - a\circ f(x) + a.
\end{equation}
Let $g(x) = \widetilde{g}(x) + C$. Assume that the real-valued constants $C$ and $a$ are unknown. Furthermore, note that (see Theorem xx):
\begin{equation}
\int_{a'}^{b'} f(x)\,dg(x) = \int_{a'}^{b'}f(x)\,\widetilde{g}(x), 
\end{equation}
At first, it seems impossible to compute $a(y)$ given $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 
\begin{equation}
\label{eq:implies}
g(a') = \widetilde{g}(a') + C \implies C = a - \widetilde{g}(a'). 
\end{equation}
Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_def2} eliminates
both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
\begin{equation}
a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
\end{equation}
We can now compute the following:
\begin{itemize}
\item Compute $a = a(0)$.
\item Compute $C = a - \widetilde{g}(a')$.
\item Compute $g(x) = \widetilde{g}(x) + C$.
\item Compute $h(x) = g^{-1}(x)$.
\item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
\end{itemize}
It now follows that 
\begin{equation}
\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x):=\int_{a(y)}^{b(y)}f(x)dx. 
\end{equation}
The above derivation implies that not every Riemann-Stieltjes integral can be converted into a Cavalieri integral. It, however, does tell us that every Riemann-Stieltjes integral can be converted into an equivalent Riemann-Stieltjes integral, which in turn, can be converted into a Cavalieri integral. The latter Riemann-Stieltjes integral is obtained by computing the constant $C$. These concepts are clarified in Section~\ref{} via a worked out example.

The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section. The functions 
$g(x)$, and $f(x)$ now also need to be differentiable and invertable. Moreover, $a(0)$ must exist. These assertions are deemed to be true for the remainder of the paper and as such are not repeated again. As will become clear later on, these restrictions limit the number of fractional integrals for which the geometric framework we propose in this paper can produce meaningful results. This, however, does not diminish the importance of the proposed framework, since, for the integrals for which the framework does produce meaningful results, we gain valuable and novel insights.

@@

\section{Cavalieri Integral: Clarifying Example}
\label{sec:cav_integral_example}
The example which we present below was taken from \cite{?}. Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is depicted in Fig.~\ref{fig:caval2}.\\
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.3\textwidth]{fig12}
%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
%\label{fig:ex1}
%\end{figure}
%\begin{figure}[htb]
%\centering
%\includegraphics[width=0.75\textwidth]{fig13.pdf}
%\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$. The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:cav_sum}). Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
%\label{fig:caval2}
%\end{figure}

@@

We can approximate the area of $R$ by using rectangular integration strips. It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$. Moreover, the sides of the aforementioned integration strips need to be tranlsations of the function $a(y)$.

>>>>

 \title[VISUALIZATION OF FRACTIONAL INTEGRALS]{VISUALIZATION OF THE LEFT-SIDED RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL}
 \author[\normalsize V. Kiryakova, S. Author]{\normalsize Virginia Kiryakova $^1$, Second Author $^2$}

@@

%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}In this paper we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral. We found that a Riemann-Liouville integral can be thought of as the area obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the integral's order of integration and its upper integration limit. This geometric interpretation is quite useful from a pedagogical perspective as it is very similar
in nature to the geometric interpretation of the Riemann integral.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%% Section 1 %%%%%%%%%%%%%
% %\section{Introduction}\label{Sec:1}
% 
% \section{First section of the paper}\label{sec:1}
% 
% \setcounter{section}{1}
% \setcounter{equation}{0}\setcounter{theorem}{0}
% 
% 
% Text ... (for details, see \cite{GasRah}, \cite{Rosbl}, \cite{Kir},
% \cite{Moak}) ...
% 
% %%%% example of definition %%%%
%  \begin{definition}\label{Def3}
% Text of Definition~\ref{Def3}.
%  \end{definition}
% 
%    \vspace*{-12pt} %%% example of subsection:
%  \subsection{Preliminary results}\label{subsec:1.1}
% 
% %%%% example of theorem %%%%%%%%%%
%  \begin{theorem}\label{Th1}
% Text of Theorem~\ref{Th1} ....
%  \end{theorem}
% 
%  \proof %%%%%%%%%%%%%
%  Give here the proof of Theorem~\ref{Th1}. Example for
% equation:
% \begin{equation}\label{eq1}
% ax^2+bx +c =0.
% \end{equation}
%  As seen by equation \eqref{eq1}, it is ...
%  The proof follows from Ref. \cite{Moak}.
%  \proofend %%%%%%%%%%
% 
% %%%% example of corollary %%%%
%  \begin{corollary}\label{Cor2}
% Text of Corollary~\ref{Cor2} ....
%  \end{corollary}
% 
%  \proof
%  Here comes the proof of Corollary~\ref{Cor2}.
%  \proofend
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Second section of the paper}\label{sec:2}
% 
% \setcounter{section}{2}
% \setcounter{equation}{0}\setcounter{theorem}{0}
% 
% 
%  Text ... As seen in Section~\ref{sec:1}, the equation
% (\ref{eq1}), $ a\neq 0$, has the solutions
%  \begin{equation}\label{eq2}
%  x_{1,2}= {\frac {-b \pm \sqrt{b^2-4ac}}{2a}}\,.
%  \end{equation}
% 
%  %%% example of example %%%%%
%  \begin{example}\label{Ex1}
%  Let us take in (\ref{eq2}) ... Then, by Theorem~\ref{Th1}, ...
%  \end{example}
% 
%  \begin{example}\label{Ex2}
%  Under same conditions as in Example~\ref{Ex1}, we consider ...
%  \end{example}
% 
% 
% The figures should be input in the LaTeX file as eps-files, as below:
% 
% %%%%%%%%% example for figure %%%%%%%%%%%%%%%%%%%
%   \begin{center}
%   \includegraphics[scale=0.4]{figure.eps}
%  % \hspace*{2cm}
%  % \includegraphics[scale=0.7]{figure2.eps}
% 
%  \bigskip
% 
%   Figure 2.1: Control loop
%   \end{center}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
%  Often figures include texts or Latin, Greek etc. letters.
%  We kindly ask the authors to take care that no texts fonts need to be embedded, by saving first the text as curves.
%  Just in case, along with the obligatory eps-files, please send us also some alternative figures' files in  pdf-, jpg-, etc. format.

\section{Introduction}
%Leibniz, who is regarded by many scholars as the father of calculus, is credited with inventing the following notation: $\frac{d^n y}{d x^n}$. 
%A natural question which arises when one inspects this notation is: Can $n$ be a non-integer value? L'Hospital phrased it differently: ``\emph{What if $n$ be a $\frac{1}{2}$?}''. 
%In a letter Leibniz sent to L'Hospital, Leibniz comments on L'Hospital's question by making the following prophetic remark: ``\emph{This is an apparent paradox from which, one day, useful 
%consequences will be drawn}'' \cite{ross77,machado14,machado17}.\\

\noindent
The mathematical discipline in which we study the extension of derivatives and integrals to non-integer orders is known as fractional calculus. Euler, Liouville and Riemann laid most 
of the theoretical groundwork, which was needed to develop the field of fractional calculus \cite{davis59,euler1738,liouville1832,riemann1876,laurent1884}. Fractional calculus has now developed into a mature discipline \cite{machado14,machado17}. 
However, there is one aspect of the discipline which only started to develop fairly recently: its physical and geometric interpretability. At the first international conference on fractional calculus in
New Haven (USA) (which took place in 1974) it was pointed out that literature lacked an acceptable geometric and physical interpretation of fractional calculus \cite{ross06}. Subsequently, the last few decades have seen 
a number of papers that attempt to rectify this. There now exist probabilistic interpretations \cite{stanislavsky04,machado03}, geometric interpretations \cite{adda97,tarasov16,podlubny02}, physical interpretations \cite{cioc16,rutman95, nigmatullin92, gomez14} and economic 
interpretations \cite{tarasova17} of fractional order integrals and differentials.\\

\noindent
In this article we specifically focus on the geometric interpretation of fractional integrals. To be more specific, we present a novel geometric interpretation of the left-sided Riemann-Liouville fractional integral based at $a'$ \cite{laurent1884}.
As we mentioned earlier, Riemann and Liouville played an important role in the development of fractional calculus. Their work was crucial in defining what is now known as 
the Riemann-Liouville fractional integral \cite{laurent1884}. At this point in time the reader should be made aware of the fact that there exists many other accepted fractional integral definitions in the literature.
We, however, deem these definitions to be beyond the scope of the current article and as such we do not discuss them any further in this work. Furthermore, the geometric interpretation 
we present here is an extension of the geometric interpretation presented by Podlubny \cite{podlubny02}. Podlubny showed that a Riemann-Liouville fractional integral 
can be converted into a Riemann-Stieltjes integral. Moreover, Grobler showed that a Riemann-Stieltjes integral can be interpreted as the area which is obtained by summing together 
the area of an infinite number of non-rectangular infinitesimals, i.e. a Riemann-Stieltjes integral can be converted into a Cavalieri integral \cite{ackermann12,grobler19}. Combining these two ideas results in the following geometric 
interpretation: the Riemann-Liouville fractional integral can be interpreted as the area which is obtained by summing together the area of an infinite number of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $t$.\\

\noindent
We start the paper by reviewing the definition of the Riemann-Stieltjes integral, the Cavalieri integral and the left-sided Riemann-Liouville fractional integral. We then present Podlubny's original geometric framework, followed by our novel geometric framework. We end the paper with two examples and a conclusion.

\section{Riemann-Stieltjes integral}
\label{sec:rs}
\noindent
Let $f$ and $g$ denote real-valued functions defined on a closed interval $[a',b']$ of the real line. We shall suppose that both $f$ and $g$ are bounded on $[a',b']$. Recall that the Riemann-Stieltjes integral is defined as follows \cite{bartle76}:
\begin{equation}
\label{eq:g_int2}
\int_{a'}^{b'} f(x) dg(x) =  \lim_{n \rightarrow \infty}\sum_{i=0}^{n-1} f(x_i)[g(x_{i+1})-g(x_{i})], 
\end{equation}
with $(x_i)_{i=0}^n$ being arbitrary partition points on the $x$-axis. 
The function $g$ is known as the integrator and if it is monotone increasing then it maps points in the interval $[a',b,]$ to the interval $[a,b]$, with $a = g(a')$ and $b = g(b')$. The integral in equation~\eqref{eq:g_int2} is hard to evaluate in its present form. If $g$ is differentiable, however, then it becomes trivial to 
evaluate a Riemann-Stieltjes integral due to the following identity:
\begin{equation}
\label{eq:rs_identity}
\int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)~dx.
\end{equation}

% \begin{definition}
% Define a partition $\mathcal{P}$ of $[a',b']$ to be a set of points $x_0, x_1,\cdots,x_n$, 
% where $a' = x_0 \leq x_1 \leq \cdots \leq x_n = b'$. For each partition 
% $\mathcal{P}$ of $[a',b']$ write $\Delta g_k = g(x_k)-g(x_{k-1})$. Let 
% $M_k = \sup\{f(x),x_{k-1}\leq x \leq x_{k}\}$, $m_k = \inf\{f(x),x_{k-1}\leq x \leq x_{k}\}$, and set 
% \begin{equation}
% \label{ref:S_up}
% \mathcal{S}_U(\mathcal{P},f,g) = \sum_{k=1}^n M_k \Delta g_k, 
% \end{equation}
% and
% \begin{equation}
% \label{ref:S_low}
% \mathcal{S}_L(\mathcal{P},f,g) = \sum_{k=1}^n m_k \Delta g_k. 
% \end{equation}
% The sums in equation~\eqref{ref:S_up} and equation~\eqref{ref:S_low} are respectively called the the upper and lower Riemann-Stieltjes sums.
% If there is a unique number $I$ that satisfies the inequality $\mathcal{S}_L(\mathcal{P},f,g)\leq I \leq \mathcal{S}_U(\mathcal{P},f,g)$ for all 
% partitions $P$ of $[a',b']$, then $f$ is Riemann integrable with respect to $g$ on $[a',b']$. Moreover, $I$ is called the Riemann-Stieltjes integral of $f$ from $a'$ to $b'$ and is denoted by
% \begin{equation}
% \int_{a'}^{b'} f(x) dg(x). 
% \end{equation}
% \end{definition}
% 
% \begin{theorem}
% If the derivative $g'$ exists and is continuous on $[a',b']$ and if $f$ is integrable with respect to $g$ on $[a',b']$, then the following 
% Riemann and Riemann-Stieltjes integrals are equivalent
% \begin{equation}
% \int_{a'}^{b'} f(x) dg(x) = \int_{a'}^{b'} f(x)g'(x)dx.
% \end{equation}
% \end{theorem}

@@

\noindent
Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
integration strip is calculated using Cavalieri's principle. Cavalieri's principle is stated below without proof:

\begin{theorem}
Suppose two regions in a plane are included between two parallel lines in that plane. If every line parallel to these two lines intersects both regions in line segments of equal length, then the two regions have equal areas \cite{??}. 
\end{theorem}

The definition of the Cavalieri integral is presented in Definition~\ref{def:cav_integral}. It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{sec:cav_integral_example} instead. The reader who is not familiar with the Cavalieri integral should only refer back to the definitions presented in this section when things in Section~\ref{sec:cav_integral_example} become unclear. Moreover, the definitions presented below were taken from \cite{??}. Furthermore, none of the theorems in this section are proved, the proofs can be found in \cite{??}.

@@

\noindent
Let $a(y)$ be a translational function with respect to a function $f(x)$ on the interval $[a,b]$. Moreover, $b(y) = a(y) + (b-a)$. Furthermore, the functions $a(y)$ and $b(y)$ intersect $f(x)$ at $a'$ and $b'$ respectively. These assertions are assumed to be true throughout the paper and will not be repeated again.

@@

\noindent
The functions $h(x)$ and $g(x)$ are known as the transformation function and the inverse transformation function, respectively. Furthermore,
\begin{equation}
\label{eq:g_def}
g(x) = x - a\circ f(x) + a 
\end{equation}
and
\begin{equation}
\label{eq:h_def}
h(x) = g^{-1}(x). 
\end{equation}

\begin{definition}\label{def:cav_integral}
Define a partition $\mathcal{P}_1$ of $[a,b]$ to be a set of points $x_0^1, x_1^1,\cdots,x_n^1$, 
where $a = x_0^1 \leq x_1^1 \leq \cdots \leq x_n^1 = b$. For each partition 
$\mathcal{P}_1$ of $[a,b]$ write $\Delta x_k^1 = x_k^1-x_{k-1}^1$. 
%Since both boundaries of any integration strip are necessarily
%translations of the translational function $a(y)$, we can apply the transformation
%function $h$ to the partition $\mathcal{P}_1$. 
If the transformation function $h$ is strictly increasing,
the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. It
can be assumed that $h$ is strictly increasing, without any loss of generality.  Let 
$M_k = \sup \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, $m_k = \inf \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, and set 
\begin{equation}
\label{eq:c_up}
\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k^1, 
\end{equation}
and
\begin{equation}
\label{eq:c_low}
\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k^1. 
\end{equation}
The sums in equation~\eqref{eq:c_up} and equation~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{C}_L(\mathcal{P}_1,f,h)\leq I \leq \mathcal{C}_U(\mathcal{P}_1,f,h)$ for all 
partitions $\mathcal{P}_1$ of $[a,b]$, then $I$ is called the Cavalieri integral of $f$ from $a(y)$ to $b(y)$ and is denoted by
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx.
\end{equation}
\end{definition}

\noindent
Note that the superscripts of the $x$-coordinates in the above definitions indicate to which partition, either $\mathcal{P}_1$ or $\mathcal{P}_2$, the $x$-coordinate in question belongs.

\begin{theorem}
\label{t:conv}
The following Cavalieri, Riemann, and Riemann--Stieltjes integrals are equivalent:
\begin{equation}
\int_{a(y)}^{b(y)} f(x)\,dx = \int_a^b f\circ h(x)\,dx = \int_{a'}^{b'} f(x)\,dg(x).
\end{equation}
\end{theorem}

\noindent
Theorem~\ref{t:conv} tells us how to convert a Cavalieri integral into an equivalent Riemann or Riemann-Stieltjes integral. It, however, tells us nothing about the reverse 
procedure, if we are given a Riemann-Stieltjes integral how do we convert it into a Cavalieri integral?\\

\noindent
Consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$. Assume that $\widetilde{g}(x)$ is a differentiable and invertable real-valued function on $[a',b']$. How do we go about converting $\int_{a'}^{b'} f(x)\,\widetilde{g}(x)$ into a Cavalieri integral? Note that for all $K\in\mathbb{R}$ (see equation~\ref{eq:rs_identity}):
\begin{equation}
\int_{a'}^{b'} f(x)\,d[\widetilde{g}(x)+K] = \int_{a'}^{b'}f(x)\,\widetilde{g}(x). 
\end{equation}
Furthermore, recall that
\begin{equation}
\label{eq:g_definition}
g(x) = x - a\circ f(x) + a.
\end{equation}
Moreover, let $C$ be a unique real-valued constant that satisfies: $g(x) := \widetilde{g}(x)+C$. At first, it does not seem possible to compute $a(y)$ (perform the required conversion) given only $\widetilde{g}(x)$ as $C$ and $a$ are unknown a priori. However, 
\begin{equation}
\label{eq:implies}
g(a') = \widetilde{g}(a') + C \implies C = a - \widetilde{g}(a'). 
\end{equation}
Substituting Equation~\eqref{eq:implies} into Equation~\eqref{eq:g_definition} eliminates both $a$ and $C$ from it. If we then solve for $a(y)$ we obtain:
\begin{equation}
a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
\end{equation}
We can now compute the following:
\begin{itemize}
\item Compute $a = a(0)$.
\item Compute $C = a - \widetilde{g}(a')$.
\item Compute $g(x) = \widetilde{g}(x) + C$.
\item Compute $h(x) = g^{-1}(x)$.
\item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
\end{itemize}
It now follows that: 
\begin{equation}
\int_{a'}^{b'} f(x)d\,\widetilde{g}(x) = \int_{a'}^{b'} f(x)d\,g(x):=\int_{a(y)}^{b(y)}f(x)dx. 
\end{equation}
The above derivation implies that that not every Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,\widetilde{g}(x)$ can directly be converted into a Cavalieri integral. We normally need to first convert it into an equivalent Riemann-Stieltjes integral $\int_{a'}^{b'} f(x) d\,g(x)$. The Riemann-Stieltjes integral so obtained can then be converted into a Cavalieri integral. The former conversion is achieved by computing the real-valued constant $C$. Once, $C$ is known the latter conversion follows trivially. The above steps should be clearer to the reader once they have worked through the example presented in Section~\ref{sec:cav_integral_example}.\\

%not every Riemann-Stieltjes integral can be converted into a Cavalieri integral. It, however, does tell us that every Riemann-Stieltjes integral can be converted into an equivalent Riemann-Stieltjes integral, which in turn, can be converted into a Cavalieri integral. The latter Riemann-Stieltjes integral is obtained by computing the constant $C$. The above steps should be clearer to the reader once they have worked through the example in Section~\ref{}.

\noindent
The theorems and definitions presented in this section impose much greater restrictions on $g(x)$ and $f(x)$ than that mentioned in the begining of Section~\ref{sec:rs}. The functions $g(x)$ and $f(x)$ now also need to be differentiable and invertable. Moreover, $a(0)$ must exist. These additional restrictions on $f(x)$ and $g(x)$ are assumed to be true for the remainder of the paper and as such are not repeated again.

%As will become clear later on, these restrictions limit the number of fractional integrals for which the geometric framework we propose later on can produce meaningful results. Generally speaking, however, it does improve our understanding of fractional integration.

@@

\section{Cavalieri Integral: Clarifying Example}
\label{sec:cav_integral_example}
\noindent
The example which we present below was taken from \cite{?}. Let the region $R$ be bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$ and $b(y)=4-y$. This region is depicted in Figure~\ref{fig:caval2}.\\

\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{fig13.pdf}
\caption{Region bounded by the $x$-axis and the lines $f(x)=x$, $a(y)=1-y$, and $b(y)=4-y$. In the case of $R$: $a=1$, $b=4$, $a'=\frac{1}{2}$ and $b'=2$. The figure also depicts the partition points $x_i^2$ as used in the Cavalieri sum (see Equation~\eqref{eq:cav_sum}). Reproduced from Quaestiones Mathematicae (2012) 35: 265-296 with permission \copyright~ NISC (Pty) Ltd.}
\label{fig:caval2}
\end{figure}

@@

\noindent
We can approximate the area of $R$ by using rectangular integration strips. It, however, seems much more straightforward to approximate the area of $R$ via non-overlapping non-rectangular integration strips that toghether inscribe $R$. This can only be accomplished if the sides of the aforementioned integration strips are tranlsations of the function $a(y)$.\\
